Cycles of the logistic map

### 2013-05-07 doc/pc-ijbc.tex
add scripts in the data directory

\begin{abstract}
%\abstract{
%
The onset and bifurcation points of the $n$-cycles of
  a polynomial map are located
  through a characteristic equation
  connecting the cyclic polynomials of the cycle points.
The minimal polynomials of the critical parameters
  of the logistic, H\'enon, and cubic maps are obtained
  for $n$ up to 13, 9, and 8,
  respectively.
%
%}
\end{abstract}

@@

\twocolumn
%
%
\section{Introduction}
%
%

@@

The odd parity, however, allows us to limit
  the set of cube-free cyclic polynomials
  to those of even degrees in $\vx$.
%
This is because \refeq{cubreplace} contains only linear and cubic terms,
and a cyclic polynomial with an odd (even) degree in $\vx$
can never be reduced to one with an even (odd) degree.
%
%Thus, we only need polynomials of even degrees.
%
%We therefore have a theorem similar to \refthm{sqrfree}.
%%
%%
%\begin{theorem}
%  For the cubic map \refeq{cubic},
%  any cyclic polynomial $K(\vx)$ of
%  an $n$-cycle orbit
%  $\vct x = \{x_1, \ldots, x_n\}$
%  with an even degree in $\vct x$
%  is a linear combination of
%the even cube-free cyclic polynomials $C_p(\vx)$:
%\[
%  K(\vx) = \sum_{p \in \Pset} f_p(R) C_p(\vx),
%\]
%  where $\Pset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
%  the set of indices of all even cube-free cyclic polynomials,
%  and $f_p(R)$ are polynomials of $R$.
%  \label{thm:cubfree}
%\end{theorem}
%
%
%
%
With the above change, the rest derivation is similar to that of the logistic map.
The new $\Lambda(\vx)$ should be
$\prod_{k=1}^n f'(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
%
The polynomials of $r$
  at the onset and bifurcation points
%for some small $n$ are shown in \reftab{cubpolygen} (general $\lambda$)
%and \reftab{cubpoly} ($\lambda = \pm1$);
%for larger $n$ up to 8,
%we have saved the data
  are listed on the website in \refsec{end}.
%
The representative $r$ values are listed in \reftab{crval}.
%
%For complex $r$ and $\vx$,
%we have plotted \reffig{cubbulb} for regions of stability.

@@

%\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
%  Bailey, D. H. \& Broadhurst, D. J. [2000]
%  ``Parallel integer relation detection: techniques and applications,''
%  {\it Mathematics of Computation}
%  \textbf{70},
%  1719--1736.

\bibitem[Bailey {\it et al.}(2006)]{bailey}
  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
  ``Ten problems in experimental mathematics,''
  {\it The American Mathematical Monthly}
  \textbf{113},
  481--509.

>>>>

\begin{abstract}
The onset and bifurcation points of the $n$-cycles of
  a polynomial map are located
  through a characteristic equation
  connecting the cyclic polynomials of the cycle points.
The minimal polynomials of the critical parameters
  of the logistic, H\'enon, and cubic maps are obtained
  for $n$ up to 13, 9, and 8,
  respectively.
\end{abstract}

@@

% switch text to two-column
\twocolumn

%
%
\section{Introduction}
%
%

@@

The odd parity, however, allows us to limit
  the set of cube-free cyclic polynomials
  to those of even degrees in $\vx$.
%
This is because \refeq{cubreplace} contains only linear and cubic terms,
and a cyclic polynomial with an odd (even) degree in $\vx$
can never be reduced to one with an even (odd) degree.
%
%Thus, we only need polynomials of even degrees.
%
%We therefore have a theorem similar to \refthm{sqrfree}.
%%
%%
%\begin{theorem}
%  For the cubic map \refeq{cubic},
%  any cyclic polynomial $K(\vx)$ of
%  an $n$-cycle orbit
%  $\vct x = \{x_1, \ldots, x_n\}$
%  with an even degree in $\vct x$
%  is a linear combination of
%the even cube-free cyclic polynomials $C_p(\vx)$:
%\[
%  K(\vx) = \sum_{p \in \Pset} f_p(R) C_p(\vx),
%\]
%  where $\Pset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
%  the set of indices of all even cube-free cyclic polynomials,
%  and $f_p(R)$ are polynomials of $R$.
%  \label{thm:cubfree}
%\end{theorem}
%
%
%
%
With the above change, the rest derivation is similar to that of the logistic map.
The new $\Lambda(\vx)$ should be
$\prod_{k=1}^n f'(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
%
The polynomials of $r$
  at the onset and bifurcation points
%for some small $n$ are shown in \reftab{cubpolygen} (general $\lambda$)
%and \reftab{cubpoly} ($\lambda = \pm1$);
%for larger $n$ up to 8,
%we have saved the data
  are listed on the website in \refsec{end}.
%
The representative $r$ values are listed in \reftab{crval}.
%

@@

%\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
%  Bailey, D. H. \& Broadhurst, D. J. [2000]
%  ``Parallel integer relation detection: techniques and applications,''
%  {\it Mathematics of Computation}
%  \textbf{70},
%  1719--1736.
%
\bibitem[Bailey {\it et al.}(2006)]{bailey}
  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
  ``Ten problems in experimental mathematics,''
  {\it The American Mathematical Monthly}
  \textbf{113},
  481--509.
